Incentivizing Exploration by Heterogeneous Users

### 2018-06-06 result_discussion.tex

When $\TieDensity = 0$, the bound of Theorem~\ref{rst:regret} is
constant in $T$;
thus, the algorithm achieves constant regret using constant
expected payments. 
As discussed in Section~\ref{sec:prob},
the case $\TieDensity = 0$ arises, for instance, for
discrete agent distributions.
In fact, in the case of a discrete agent distribution,
it is possible to modify the algorithm to also
reduce the dependence on \MinProb from exponential to polynomial.
Theorem~\ref{rst:discrete} (given later) states that the modified
algorithm achieves expected regret
$O \left(\frac{\ARMNUM}{\MinProb^4} \right)$
with expected payments of
$O \left(\frac{\ARMNUM^2}{\MinProb^{5/2}} \right)$.

>>>>

When $\TieDensity = 0$, the bound of Theorem~\ref{rst:regret} is
constant in $T$;
thus, the algorithm achieves constant regret using constant
expected payments. 
As discussed in Section~\ref{sec:prob},
the case $\TieDensity = 0$ arises, for instance, for
\dkdelete{discrete} agent distributions \dkedit{with finite support}.
\dkdelete{In fact, in the case of a discrete agent distribution,}
\dkedit{Alternatively, when $\TieDensity = 0$, 
one can modify} the algorithm to
reduce the dependence on \MinProb from exponential to polynomial,
\dkedit{at the cost of reintroducing the poly-logarithmic dependence
  on $T$}.
Theorem~\ref{rst:discrete} (given later) states that the modified
algorithm achieves expected regret
$O \left(\frac{\ARMNUM}{\MinProb^4} \right)$
with expected payments of
$O \left(\frac{\ARMNUM^2}{\MinProb^{5/2}} \right)$.
\dkcomment{Adjust these bounds.}
\dkedit{Whether one can achieve regret that is simultaneously
  independent of $T$ and polynomial in \ARMNUM and \MinProb is an
  interesting open question.}
